Estimation of the road traffic sound levels based on the Semi-Supervised Non-Negative Matrix Factorization of Magnitude Spectrograms

### 2017-10-19 article/articleApplied.tex
starting results

The experiment consists in estimating the traffic road sound level on the environmental sound corpus. NMF is used and compared to a simple approach which consist in a frequency low-pass filter (this second method relies on the fact that road traffic is mainly composed of low frequencies, compared to main of the confounded sounds (voices, birds, etc.)) with the cut-off frequency $f_c$. The spectrogram $\mathbf{V}$ is built with a window size $w = 2^{14}$ with a 75 $\%$ overlapping and a number of point $nfft = 2^{14}$. Therefore, the dimensions of $V$ are $F$ = 8192 and $N$ = 772.  Similarly, the frequency low-pass filter is applied on the spectrogram $\mathbf{V}$ and on the dictionary $\mathbf{W}$ ( renamed $\mathbf{V}_{f_c}$ and $\mathbf{W}_{f_c}$ respectively). The aim to focus the reconstruction of the signal on the frequencies where the traffic components are. The figure \ref{fig:block_diagram_protocol} summarizes the different steps of the process depending on the chosen method, which consist of 3 steps:

@@

The dictionary is built from a sound database dedicated specially to this task. It is composed of 53 audio files of car passages. First, for each audio file, its spectrogram is calculated with fixed parameters ($w$, 75 $\%$ overlap, $nfft$). Then a temporal rectangular window is applied without overlapping on the spectrogram in order to consider several spectrum for each audio file. The size of the window is set up at 0.5 and 1 second. In each window, the root mean square value is calculated on each frequency bin to reduce the different spectrum in one spectra.  An example that illustrates the process can be found on figure \ref{fig:dictionaryExtraction} in the ease of a large window of 4 seconds.

\begin{figure}[!t]
\centering
	\begin{minipage}[t]{.24\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../image/extractionDictionary1Example.pdf}
	\end{minipage}
	\begin{minipage}[t]{.24\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../image/extractionDictionary2Example.pdf}
	\end{minipage}
	\caption{Example of the extraction of the spectrum with a 1 second window. On left, the original spectrogram with the temporal window, on the left, the 4 spectrum obtained (dB scale)}
	\label{fig:dictionaryExtraction}
\end{figure}

However, the number of elements got on all the sound database does not respect the constraint imposed about the dimension of NMF ($F \times K + K \times N < F \times N$). With a 1 second window, $K$ = 1003. In consequence, a $K$-medoid clustering is applied to reduce the number of spectrum to $K = \left[ 25, 50, 100 \right]$. A special case is added where the root mean square of \textit{all} the spectrogram is applied. One spectra is then generated by audio file.
Each element is normalized such as $\vert \vert \mathbf{W_k} \vert \vert = 1$ with $\vert \vert \bullet \vert\vert$ is the $\ell-1$ norm. Table \ref{tab:dictionary_factors} summarizes the parameters and their related values.

@@

\paragraph{NMF}\mbox{} \\
The second estimator is supervised and semi-supervised NMF (see part \ref{part:nmf}). The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed on two different formats: with a linear frequency scale ($\Delta f \approx 2.8$ Hz) and with third octave bands (27 bands). Theses two methods enable to compare a fine approach (the linear scale) with a degraded one (the third octave bands) as it reduces the number of frequency bins and allows to reduces the number of bands in the high frequencies where the traffic component is less present. NMF is performed on 400 iterations which is sufficiently enough to get a stabilized reconstruction. Furthermore, in the case of the linear frequency scale, $\mathbf{V}$ and $\mathbf{W}$ are filtered at the frequencies $f_c$ in order to focused the reconstruction of the signal of the low frequency bins. In consequence, if NMF is performed with filtered elements ($\mathbf{V}_{f_c}$ and $\mathbf{W}_{f_c}$) to determine $\mathbf{H}_{f_c}$, the traffic signal reconstruction is made with the original dictionary $\mathbf{W}$, as

@@

\subsubsection{Metric}
The performances of the two estimators of the road traffic sound level are assessed through the calculation of two metrics.

@@

with $T$ is the number of temporal bin in the signal. The linear scale is here more relevant as it is more sensitive to the error on the high sound levels than the dB scale. Then for one combination of factors, the $N$ $nRMSE$ calculated are averaged.\\
\end{itemize}

@@

>>>>

The experiment consists in estimating the traffic road sound level on the environmental sound corpus built using the simulation tool. NMF is used and compared to a baseli,e approach which consist in a frequency low-pass filter as road traffic is mainly composed of low frequencies, compared to main of the intefereing. this baseline has one parameter being the cut-off frequency $f_c$.

The spectrogram $\mathbf{V}$ is built with a window size $w = 2^{14}$ with a 75 $\%$ overlapping and a number of point $nfft = 2^{14}$. Therefore, the dimensions of $V$ are $F$ = 8192 and $N$ = 772.  Similarly, the frequency low-pass filter is applied on the spectrogram $\mathbf{V}$ and on the dictionary $\mathbf{W}$ ( renamed $\mathbf{V}_{f_c}$ and $\mathbf{W}_{f_c}$ respectively). This to focus the NMF estimation of the signal on the frequencies where the traffic components are most present. The figure \ref{fig:block_diagram_protocol} summarizes the different steps of the process depending on the chosen method, which consist of 3 steps:

@@

The dictionary is built from a sound database dedicated specifically to this task. It is composed of 53 audio files of passing cars. First, for each audio file, its spectrogram is calculated with fixed parameters ($w$, 75 $\%$ overlap, $nfft$). Then a temporal rectangular window \ml{pourquoi pas de fenetrage ?} is applied without overlapping on the spectrogram in order to consider several spectrum for each audio file. The size of the window is set up at 0.5 and 1 second. In each window, the root mean square value is calculated on each frequency bin to reduce the different spectrum in one spectra.  An example that illustrates the process can be found on figure \ref{fig:dictionaryExtraction} in the ease of a large window of 4 seconds.

\begin{figure}[!t]
\centering
	\begin{minipage}[t]{.24\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../image/extractionDictionary1Example.pdf}
	\end{minipage}
	\begin{minipage}[t]{.24\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../image/extractionDictionary2Example.pdf}
	\end{minipage}
	\caption{Example of the computation of the spectrum with a 1 second window. On left, the original spectrogram with the temporal window, on the left, the 4 spectrum obtained (dB scale)}
	\label{fig:dictionaryExtraction}
\end{figure}

Since the number of elements given by porcessing all the sound database does not respect the constraint imposed about the dimension of NMF ($F \times K + K \times N < F \times N$), a $K$-medoid clustering is applied to reduce the number of spectrum to $K = \left[ 25, 50, 100 \right]$. A special case is added where the root mean square of \textit{all} the spectrogram is applied. One spectra is then generated by audio file. \ml{pas clair}
Each element is normalized such as $\vert \vert \mathbf{W_k} \vert \vert = 1$ with $\vert \vert \bullet \vert\vert$ is the $\ell-1$ norm. Table \ref{tab:dictionary_factors} summarizes the parameters and their related values.

@@

\paragraph{NMF}\mbox{} \\
The second estimator is supervised and semi-supervised NMF (see part \ref{part:nmf}). The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed on two different formats: with a linear frequency scale ($\Delta f \approx 2.8$ Hz) and with third octave bands (27 bands). Theses two methods are considered to compare a fine grain approach (the linear scale) with a coarser one (the third octave bands) as it reduces the number of frequency bins and allows to reduces the number of bands in the high frequencies where the traffic component is less present. NMF inference is performed for 400 iterations which is sufficiently enough to get a stabilized reconstruction. Furthermore, in the case of the linear frequency scale, $\mathbf{V}$ and $\mathbf{W}$ are filtered at the frequencies $f_c$ in order to focused the reconstruction of the signal of the low frequency bins. As a consequence, if NMF is performed with filtered elements ($\mathbf{V}_{f_c}$ and $\mathbf{W}_{f_c}$) to determine $\mathbf{H}_{f_c}$, the traffic signal reconstruction is done with the original dictionary $\mathbf{W}$, as

@@

\subsubsection{Metrics}
The performances of the two estimators of the road traffic sound level are assessed through the calculation of two metrics.

@@

where $T$ is the number of temporal bin in the signal. The linear scale is here more relevant as it is more sensitive to the error on the high sound levels than the dB scale. Then for one combination of factors, the $N$ $nRMSE$ calculated are averaged.\\
\end{itemize}

@@

\ml{la section resultats disctue des resultats, ne pas etre lineaire, genre on fait  puis on fait ca...}
